Growing libraries of concepts with wake-sleep program induction

### 2018-07-23 talk.tex
Animated unfolding of DreamCoder with figures

>>>>

\begin{frame}{EC --- Wake}
  \only<1>{
    \includegraphics[width=11cm]{figures/teachDC/.inkslides-ec/slide-0.pdf}
  }
  \only<2>{
    \includegraphics[width=11cm]{figures/teachDC/.inkslides-ec/slide-1.pdf}
  }
  \only<3>{
    \includegraphics[width=11cm]{figures/teachDC/.inkslides-ec/slide-2.pdf}
  }
  \only<4>{
    \includegraphics[width=11cm]{figures/teachDC/.inkslides-ec/slide-3.pdf}
  }
  \only<5>{
    \includegraphics[width=11cm]{figures/teachDC/.inkslides-ec/slide-4.pdf}
  }

\begin{frame}{DreamCoder --- Wake}
  \only<1>{
    \includegraphics[width=11cm]{figures/teachDC/.inkslides-dc/slide-0.pdf}
  }
  \only<2>{
    \includegraphics[width=11cm]{figures/teachDC/.inkslides-dc/slide-1.pdf}
  }
  \only<3>{
    \includegraphics[width=11cm]{figures/teachDC/.inkslides-dc/slide-2.pdf}
  }
  \only<4>{
    \includegraphics[width=11cm]{figures/teachDC/.inkslides-dc/slide-3.pdf}
  }
  \only<5>{
    \includegraphics[width=11cm]{figures/teachDC/.inkslides-dc/slide-4.pdf}
  }

\begin{frame}{DreamCoder --- Sleep-G}
  \only<1>{
    \includegraphics[width=11cm]{figures/teachDC/.inkslides-sleep-g/slide-4.pdf}
  }
\end{frame}
\begin{frame}{DreamCoder --- Sleep-R-1}
  \only<1>{
    \includegraphics[width=11cm]{figures/teachDC/.inkslides-sleep-r-1/slide-4.pdf}
  }
\end{frame}
\begin{frame}{DreamCoder --- Sleep-R-2}
  \only<1>{
    \includegraphics[width=11cm]{figures/teachDC/.inkslides-sleep-r-2/slide-4.pdf}
  }
\end{frame}
